Multi-Core Model Checking and Maximum Satisfiability Applied to Hardware-Software Partitioning

### 2016-08-28 Docs/IJES/journal.tex
update reply letter

%----------------------------------------------
\subsection{Multi-core ESBMC with OpenMP (ESBMC-SS)}
\label{Multi-core-ESBMC-with-OpenMP}
%----------------------------------------------

@@

%----------------------------------------------
\subsection{Multi-core ESBMC with OpenMP using Workers (ESBMC-PS)}
\label{Multi-core-ESBMC-with-OpenMP-using-workers}
%----------------------------------------------

@@

%----------------------------------------------
\subsection{Multi-core ESBMC with OpenMP using Binary Search (ESBMC-PB)}
\label{Multi-core-ESBMC-with-OpenMP-using-Binary-Search}
%----------------------------------------------

@@

%----------------------------------------------
\subsection{\textcolor{blue}{Time Complexity of ESBMC-SS, ESBMC-PS, and ESBMC-PB}}
\label{complexity}
%----------------------------------------------

>>>>

%----------------------------------------------
\subsection{Multi-core ESBMC}
\label{Multi-core-ESBMC}
%----------------------------------------------

%----------------------------------------------
\subsubsection{Multi-core ESBMC with OpenMP (ESBMC-SS)}
\label{Multi-core-ESBMC-with-OpenMP}
%----------------------------------------------

@@

%----------------------------------------------
\subsubsection{Multi-core ESBMC with OpenMP using Workers (ESBMC-PS)}
\label{Multi-core-ESBMC-with-OpenMP-using-workers}
%----------------------------------------------

@@

%----------------------------------------------
\subsubsection{Multi-core ESBMC with OpenMP using Binary Search (ESBMC-PB)}
\label{Multi-core-ESBMC-with-OpenMP-using-Binary-Search}
%----------------------------------------------

@@

%----------------------------------------------
\subsubsection{\textcolor{blue}{Time Complexity of ESBMC-SS, ESBMC-PS, and ESBMC-PB}}
\label{complexity}
%----------------------------------------------
